---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shiny.quetzio

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

This package includes the way to create a questionnaire using various Shiny widgets
from a source file: either a local YAML file, or GoogleSheet over the net.
Results of the surveys are send to GoogleSheet of your choice.

It is all completely handled by `R6` shiny modules, so it is easy to include 
even multiple independent questionnaires in your ShinyApp and keep your code clean!

You can preview the `pkgdown` generated website [here](https://statismike.github.io/shiny.quetzio/){target="_blank"}
You can view interactive demo hosted on shinyapps [here](https://statismik.shinyapps.io/quetzio-demo/){target="_blank"}

## Installation

You can install the development version of shiny.quetzio from *GitHub* with:

``` r
# install.packages("devtools")
devtools::install_github("StatisMike/shiny.quetzio")
```
## Current features

At the current stage of development the `shiny.quetzio` package consists of two
exported `R6` classes used in server and corresponding functions to bind the
UI in your shinyApp:

* `quetzio_server` to create single questionnaire and `quetzio_UI` to input the
UI of the questionnaire. Questionnaires at the moment handles these type of inputs:
  - `textInput`
  - `numericInput`
  - `selectizeInput`
  - `radioButtons`

* `quetzio_link_server` to link multiple semi-independent questionnaires and
`quetzio_link_UI` to bind the connected UI.

>Choosing `numericInput` for item type, the object that will be generated is
actually custom input widget: `numInput`. It allows no initial value and 
placeholder text.

### In-App usage

It's usage is very straigtforward:

1. Simply add a `quetzio_server` object in your shinyApp `server()` call, and `quetzio_UI`
in your `ui`:

```{r, eval = F}
ui <- fluidPage(
  quetzio_UI("yaml_module"),
  quetzio_UI("gsheet_module")
)

server <- function(input, output, session) {

# YAML generated survey with output automatically saved to googlesheets

yaml_quetzio <- quetzio_server$new(
  source_method = "yaml",
  source_yaml = "some_yaml",
  output_gsheet_id = "googlesheet_id",
  output_gsheet_sheetname = "sheet_name_with_questions",
  module_id = "yaml_module"
)

# survey generated from googlesheet source, with output automatically saved to
# googlesheets

gsheet_quetzio <- quetzio_server$new(
  source_method = "gsheet",
  source_gsheet_id = "googlesheet_id",
  source_gsheet_sheetname = "sheet_name_with_questions",
  # you don't need to specify another googlesheet file to save answers
  # If you don't specify it, the class assumes it is the same as source one
  output_gsheet_id = "another_googlesheet_id",
  output_gsheet_sheetname = "sheet_name_with_answers",
  module_id = "gsheet_module"
)

}
```

2. Additionally, your ShinyApp can monitor the questionnaire status and react fully customizable!

```{r, eval = F}
  
# trigger some action after the questionnaire is completed
  observe({
    req(yaml_quetzio$is_done())
    showModal(
      modalDialog("You're done!")
    )
  })

# catch the answers provided to the questionnaire
  output$gsheet_answers <- renderPrint(
    gsheet_quetzio$answers()
  )

```

3. There is also a possibility to link your questionnaires in a way that they
will appear one after another with `quetzio_link_server` R6 class:

```{r, eval = F}
ui <- fluidPage(
  quetzio_link_UI("modules_link")
)

server <- function(input, output, session) {

# Linked questionnaires - one generated from yaml, second from googlesheets. 
# Their output won't be automatically saved to googlesheets in this example
# (though it is possible to set - their internal reactivity is independent
# to the quetzio_link in that regard)

  quetzio_link <- quetzio_link_server$new(
    yaml_quetzio = quetzio_server$new(
      source_method = "yaml",
      source_yaml = "some_yaml",
      module_id = "yaml_module"
    ),
    gsheet_quetzio = quetzio_server$new(
      source_method = "gsheet",
      source_gsheet_id = "googlesheet_id",
      source_gsheet_sheetname = "sheet_name_with_questions",
      module_id = "gsheet_module"
    ),
    link_id = "modules_link"
  )

  # and you can also trigger things based on the completion rate
  
  # trigger some action after the link is 50% completed and after completion
  # of both questionnaires
  observe({
    if (quetzio_link$completion() == 0.5) {
      showModal(
        modalDialog("You're half done!")
      )
    } else if (quetzio_link$completion() == 1) {
      showModal(
        modalDialog("You're completely done!")
      )
    }
  })

# catch the answers provided to the questionnaire
  output$all_answers <- renderPrint(
    quetzio_link$answers()
  )

}
```


### Survey configuration

You can configure your survey widely, using many of the features native to the
used shiny inputs. 

#### Universal parameters:

For every input you can specify:

- **inputId**
- **type**
- **label**
- mandatory: (true/false) if the input must be filled
- width: the same as in regular input specification. If not provided, defaults
to 500px

> *Bold* ones are mandatory for every input

#### Type-specific parameters:


|    parameter   |  textInput |numericInput|selectizeInput|radioButtons|
|    :----:      |   :----:   |   :----:   |    :----:    |   :----:   |
|placeholder     |      x     |     x      |              |            |    
|value           |            |     x      |              |            |    
|min             |            |     x      |              |            |    
|max             |            |     x      |              |            |    
|step            |            |     x      |              |            |    
|*choices*       |            |            |       x      |      x     |    
|*choiceValues*  |            |            |       x      |      x     |    
|*choiceNames*   |            |            |       x      |      x     |    
|maxItems        |            |            |       x      |            |    
|selected        |            |            |       x      |      x     |    
|inline          |            |            |              |      x     |    

>*Italic* parameters are interchangeable. You can specify either *choices* or both *choiceValues* and *choiceNames* for single input.

## discoRd kudos

Foundations for this package is in the 'discoRd' community. Feel free to join our 
[discoRd channel](https://discord.gg/FuTSvkSCVj){target="_blank"}!
