---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shiny.survey

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

This package includes the way to create a survey using various Shiny widgets
from a source file: either a local YAML file, or GoogleSheet over the net.
Results of the surveys are send to GoogleSheet of your choice.

It is all completely handled by `R6` shiny modules, so it is easy to include 
even multiple independend questionnaires in your ShinyApp and keep your code clean!

## Installation

You can install the development version of shiny.survey from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("StatisMike/shiny.survey")
```
## Current features

At the current stage of development the `shiny.survey` package consists of two
exported `R6` classes used in server and corresponding functions to bind the
UI in your shinyApp:
* `quetzio_server` to create single questionnaire and `quetzio_UI` to input the
UI of the questionnaire. Questionnaires at the moment handles these type of inputs:
- `textInput`
- `numericInput`
- `selectizeInput`
- `radioButtons`

* `quetzio_link_server` to link multiple semi-independent questionnaires and
`quetzio_link_UI` to bind the connected UI.


### In-App usage

It's usage is very straigtforward:

1. Simply add a `quetzio_server` object in your shinyApp `server()` call, and `quetzio_UI`
in your `ui`:

```{r, eval = F}
ui <- fluidPage(
  quetzio_UI("yaml_module"),
  quetzio_UI("gsheet_module")
)

server <- function(input, output, session) {

# YAML generated survey with output automatically saved to googlesheets

yaml_quetzio <- quetzio_server$new(
  source_method = "yaml",
  source_yaml = "some_yaml",
  output_gsheet_id = "googleSheet_id",
  output_gsheet_sheetname = "sheet_name_with_questions",
  module_id = "yaml_module"
)

# survey generated from googlesheet source, with output automatically saved to
# googlesheets

gsheet_quetzio <- quetzio_server$new(
  source_method = "gsheet",
  source_gsheet_id = "googleSheet_id",
  source_gsheet_sheetname = "sheet_name_with_questions",
  # you don't need to specify another googleSheet file to save answers
  # If you don't specify it, the class assumes it is the same as source one
  output_gsheet_id = "another_googleSheet_id",
  output_gsheet_sheetname = "sheet_name_with_answers",
  module_id = "gsheet_module"
)

}
```

2. Additionally, your ShinyApp can monitor the questionnaire status and react fully customizable!

```{r, eval = F}
  
# trigger some action after the questionnaire is completed
  observe({
    req(yaml_quetzio$is_done())
    showModal(
      modalDialog("You're done!")
    )
  })

# catch the answers provided to the questionnaire
  output$gsheet_answers <- renderPrint(
    gsheet_quetzio$answers()
  )

```

3. There is also a possibility to link your questionnaires in a way, that they
will appear one after another. It is now needed to configure your calls accordingly:

```{r, eval = F}
ui <- fluidPage(
  quetzio_link_UI("modules_link")
)

server <- function(input, output, session) {

# YAML generated survey with output automatically saved to googlesheets

  quetzio_link <- quetzio_link_server$new(
    yaml_quetzio = quetzio_server$new(
      source_method = "yaml",
      source_yaml = "some_yaml",
      module_id = "yaml_module",
      # first questionnaire will be rendered at the beginning
      render_ui = TRUE,
      link_id = "modules_link"
    ),
    gsheet_quetzio = quetzio_server$new(
      source_method = "gsheet",
      source_gsheet_id = "googleSheet_id",
      source_gsheet_sheetname = "sheet_name_with_questions",
      module_id = "gsheet_module",
      # second questionnaire will be hidden - it will be rendered only when the 
      # first has been completed
      render_ui = FALSE,
      link_id = "modules_link"
    ),
    link_id = "modules_link"
  )

  # and you can also trigger things based on the completion rate
  
  # trigger some action after the questionnaire is completed
  observe({
    if (quetzio_link$completion() == 0.5) {
      showModal(
        modalDialog("You're half done!")
      )
    } else if (quetzio_link$completion() == 1) {
      showModal(
        modalDialog("You're completely done!")
      )
    }
  })

# catch the answers provided to the questionnaire
  output$all_answers <- renderPrint(
    quetzio_link$answers()
  )

}
```


### Survey configuration

You can configure your survey widely, using many of the features native to the
used shiny inputs. 

#### Universal parameters:

For every input you can specify:

- **inputId**
- **type**
- **label**
- mandatory: (true/false) if the input must be filled
- width: the same as in regular input specification. If not provided, defaults
to 500px

> *Bold* ones are mandatory for every input

#### Type-specific parameters:


|    parameter   |  textInput |numericInput|selectizeInput|radioButtons|
|    :----:      |   :----:   |   :----:   |    :----:    |   :----:   |
|placeholder     |      x     |            |              |            |    
|value           |            |     x      |              |            |    
|min             |            |     x      |              |            |    
|max             |            |     x      |              |            |    
|step            |            |     x      |              |            |    
|*choices*       |            |            |       x      |      x     |    
|*choiceValues*  |            |            |       x      |      x     |    
|*choiceNames*   |            |            |       x      |      x     |    
|multiple        |            |            |       x      |            |    
|selected        |            |            |       x      |      x     |    
|inline          |            |            |              |      x     |    

>*Italic* parameters are interchangeable. You can specify either *choices* or both *choiceValues* and *choiceNames* for single input.

## Presentation

You can check the running demo on [shinyapps.io](https://statismik.shinyapps.io/shinysurvey_sneakpeek/){target="_blank"}

## discoRd kudos

Foundations for this package is in the 'discoRd' community, most notably users
who created the underlying logic for the  [discoRd-survey](https://github.com/discoRd-org/discoRd-survey){target="_blank"}:

- Alexander Lam ([acylam](https://github.com/acylam){target="_blank"})
- Erez Shomron ([eshom](https://github.com/eshom){target="_blank"})
- Eric Fletcher ([iamericfletcher](https://github.com/iamericfletcher){target="_blank"})

Feel free to join our great community at [discoRd channel](https://discord.gg/FuTSvkSCVj){target="_blank"}!
