---
title: "Link multiple questionnaires together"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Link multiple questionnaires together}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = F}
library(shiny.quetzio)
```

When you have created multiple questionnaires with help of the *shiny.quetzio*
already, you may wish to present them to the user sequentially - after the
completion of one it may be handy to handle another.

It can be done through the usage of *conditionalPanel* or by using the *toggle_UI*
method of *Quetzio*. It can unfortunately cause a lot of unpredicted
effects in the end, with a need for more complex logic for you to implement.

That's why the *shiny.quetzio* provides an easy way to link multiple questionnaires
together with the use of *QuetzioLink* R6 class!

>In this vignette there is an assumption that you already know how to construct
questionnaires with *Quetzio_create*. If this assumption is wrong, you should
first look into *Create a questionnaire* vignette.

## How to set up linked questionnaires

If you already know how to create a questionnaire, this will be a breeze. The 
whole procedure is analogous to one used in *Quetzio_create*.

### **server** call

You call *QuetzioLink_create* inside your *server* function.

It takes following arguments:

- **link_id** - module id of you *QuetzioLink* shiny module.
- **...** - some *Quetzio_create* calls, containing configuration
for the modules that you want to link together.
- **output_gsheet** - logical value indicating, if you want to save the results
automatically to some googlesheet. If set to *TRUE*, you will need to also
provide:
  - **output_gsheet_id** - id of the googlesheet to upload answers to
  - **output_gsheet_sheetname** - name of the spreadsheet to upload answers to

To generate linked questionnaires, we can use question sources provided with
the package (see documentation for *quetzio_examples* to get more information)

```{r quetzio_link_wo_desc, eval = F}
# assign to an object to access the state of link from you application
quetzio_link <- QuetzioLink_create(
  link_id = "linked_quetzios",
  # every questionnaire provided need to be named!
  first_quetzio = Quetzio_create(
    source_method = "raw",
    source_object = quetzio_examples$questions_lists$link_quetzio_1,
    # and you need to provide unique module ids
    module_id = "quetzio1"
  ),
  second_quetzio = Quetzio_create(
    source_method = "raw",
    source_object = quetzio_examples$questions_lists$link_quetzio_2,
    module_id = "quetzio2"
  ),
  third_quetzio = Quetzio_create(
    source_method = "raw",
    source_object = quetzio_examples$questions_lists$link_quetzio_3,
    module_id = "quetzio3"
  )
)
```

> * All module_ids and link_ids needs to be unique - just like during creation
> of regular shiny modules.
> * Remember to provide *Quetzio_create()* call directly in *...* of the *QuetzioLink_create()*.
> You cannot assign them somewhere else and provide them afterwards.

### **ui** call

To bind the interface into UI of your shinyApp, simply state following function.
It takes only one argument: *link_id*.

```{r quetzio_link_wo_desc_ui, eval = F}
# provide the same link_id as in server function
QuetzioLink_UI(
  link_id = "linked_quetzios"
)
```

## Provide instructions and item descriptions!

As with using only single *Quetzio*, you can generate title, instructions
and descriptions for individual questions. With single questionnaire you could
also build the rest of the interface by providing it directly in the code of UI
of your application.

It is much less straightforward to do with linked questionnaires - the linked
UI will be changing, and you would also need to implement logic using *shinyjs*,
*conditionalPanel* or in any other way.

Providing source for descriptions remedies it!

```{r quetzio_link_w_desc, eval = F}
# we can use the link from previous example
quetzio_link <- QuetzioLink_create(
  link_id = "linked_quetzios",
  first_quetzio = Quetzio_create(
    source_method = "raw",
    source_object = quetzio_examples$questions_lists$link_quetzio_1,
    # just provide the description source by stating either
    # 'desc_object', 'desc_yaml' or 'desc_gsheet_id' and 'desc_gsheet_sheetname'
    desc_object = quetzio_examples$description_lists$link_quetzio_1,
    module_id = "quetzio1"
  ),
  second_quetzio = Quetzio_create(
    source_method = "raw",
    source_object = quetzio_examples$questions_lists$link_quetzio_2,
    desc_object = quetzio_examples$description_lists$link_quetzio_2,
    module_id = "quetzio2"
  ),
  third_quetzio = Quetzio_create(
    source_method = "raw",
    source_object = quetzio_examples$questions_lists$link_quetzio_3,
    desc_object = quetzio_examples$questions_lists$link_quetzio_3,
    module_id = "quetzio3"
  )
)
```

## Get objects from inside of object createby by *QuetzioLink_create*

There are some objects you can get from object to which the linked questionnaires
server was assigned. Taking above assignement as example:

- **QuetzioLink$completion()** - the completion rate in form of numeric value between
0 and 1. It is generated as division: 
  - number of completed questionnaires / number of linked questionnaires
- **QuetzioLink$message()** list of *message()* of individual questionnaires
- **QuetzioLink$answers()** list of *answers()* of individual questionnaires
- **QuetzioLink$quetzio_list** gives you a way to access any element of object
from any individual *Quetzio* object.

## Updating QuetzioLink object

To update labels or selected values of items contained within *QuetzioLink*
class you can use the same functions as with singular *Quetzio*: 
**Quetzio_label_update** and **Quetzio_value_update**. You need to provide
additional argument.
To learn about these functions read vignette **Update created questionnaire**

### Reactive label update

You can update labels of any of linked questionnaires reactively with *Quetzio_label_update*
function. It works basically the same like in with *Quetzio* object, but you
need to also specify which questionnaire labels you want to update.

```{r update_labels, eval = F}
# create linked questionnaires
quetzio_link <- QuetzioLink_create(
  gender = Quetzio_create(
    source_method = "raw",
    source_object = quetzio_examples$questions_lists$gender_update,
    module_id = "updating_labels"
  ),
    quetzio_2nd = Quetzio_create(
    source_method = "raw",
    source_object = quetzio_examples$questions_lists$simple_quetzio,
    module_id = "second_in_link"
  ),
    link_id = "labels_link")

# if we have some input defined in the UI, we can update labels
# in reaction to it (in this example its inputId is 'gender')
# Its value need to be passed in a reactive object, though:
gender_react <- reactive(input$gender)

# after that - just make a call in your server
Quetzio_label_update(
  Quetzio = quetzio_link,
  name = "gender", # specify the name of questionnare
  trigger = gender_react,   # pass reactive (without parentheses!)
  source_method = "raw",   # specify source method and other args
  source_object = quetzio_examples$label_update$gender_update
)
```

You can also make something more complicated - for example get value to update 
labels of second (or any following questionnaires) on basis of answer of previous
questionnaire.

```{r update_labels within, eval=F}
quetzio_link <- QuetzioLink_create(
  gender_question = Quetzio_create(
   source_method = "raw",
   source_object = gender_1_item_source,
   module_id = "single_question"
  ),
  gender_update = Quetzio_create(
   source_method = "raw",
   source_object = quetzio_examples$questions_lists$gender_update,
   module_id = "update_gender"
  ),
  link_id = "labels_link")

# trigger need to be reactive
gender_react <- reactive({
  quetzio_link$answers()$gender_question$gender_item
})

# update labels method call
Quetzio_label_update(
  Quetzio = quetzio_link,
  # you need to provide the name of the quetzio_server in link
  # where you need to update labels
  name = "gender_update",
  # the trigger needs to be reactive, but without the parentheses
  trigger = gender_react,
  source_method = "raw",
  source_object = quetzio_examples$label_update$gender_update
)
```

### Update values of one questionnaire of the link

Method is mostly identical to *Quetzio_value_update*, though you
need to also provide *name* argument to choose which questionnaire
values you want to update.

```{r update_values, eval=F}
# update values on button press
observeEvent(input$update_vals, {
  Quetzio_value_update(
    Quetzio = quetzio_link,
    # you need to provide quetzio name in the link to update
    quetzio_name = "value_update",
    # you can use answers from one questionnaire to update another, though
    # the used values can be any other static named list
    values = quetzio_1st$answers()
    )
})
```
