---
title: "Update created questionnaire"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Update created questionnaire}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(shiny.quetzio)
```

There may be some conditions under which you would like to update rendered
questionnaire. Currently *shiny.quetzio* supports two of these updates:

- update of selected values (**Quetzio_value_update**)
- update of item labels (**Quetzio_label_update**)

In this vignette the usage of these features for *Quetzio* objects will be
described in further detail.

>This vignette assumes that the reader already knows how to create a questionnaire
with **shiny.quetzio**. Otherwise, please get this information from 'Create
a questionnaire' vignette.

## Update of selected values

I think this feature can be most beneficial in two distinct situations and 
provide option to make your questionnaire more user-friendly:

- You have one questionnaire available standalone, but it is also a part
of some linked questionnaires. User should be allowed to update the values
of linked one on the base of the standalone.
- Your shinyApp allows users to store some of their data in the external
database, and it can be retrieved in another session by them (eg. after
logging in in some matter). In this case user should be allowed to update some
of the values of the questionnaire with these.

Let's assume the values used in update are gathered from some questionnaire
made with *shiny.quetzio*, eg. some demographic data:

- using the source yaml:

    ```{yaml demographic_source, eval = F}
    gender:
      label: Which gender are you identyfing as?
      type: selectizeInput
      mandatory: true
      choiceNames:
        - Male
        - Female
        - I identify as neither of above
        - Prefer not to say
      choiceValues:
        - M
        - F
        - O
        - NI
    age:
      label: What is your age?
      type: numericInput
      mandatory: true
      min: 15
      step: 1
      placeholder: Provide integer number of years
    ```

- and code for questionnaire generation:

    ```{r demographic_questionnaire_init, eval = F}
    demo_quetzio <- Quetzio_create(
      source_method = "yaml",
      source_yaml = "path/to/yaml/file.yaml",
      module_id = "demographic_quetzio"
    )
    ```
    
- If you create afterwards a more complicated questionnaire, which will contain
items **gender** and **age** too, you can allow user to update this items with
value provided in *demo_quetzio*.
In the example below, if the user completed questionnaire assigned to **demo_quetzio**,
which contained items named the same as some items in **complex_quetzio**,
after triggering the *observeEvent* the values will be filled.

    ```{r update_from_demo, eval = F}
    # input$update is some kind of 'actionButton' to trigger the update
    
    observeEvent(input$update, {
      # call the function specifying  more complicated questionnaire,
      # in this example it is assigned to 'complex_quetzio'
      Quetzio_value_update(
        Quetzio = complex_quetzio,
        # 'values' need to be static list, therefore parenthesis are needed
        # as the 'demo_quetzio$answers' is reactiveVal object
        values = demo_quetzio$answers()
        )
    })
    ```
    
- You can also use the list populated externally of questionnaire created by
*shiny.quetzio*

    ```{r update_from_list, eval = F}
    values_to_update <- list(gender = "M",
                             age = 28)
    
    observeEvent(input$update, {
      Quetzio_value_update(
        Quetzio = complex_quetzio,
        values = values_to_update
      )
    })
    ```

## Update of item labels

There are some situations, when you would like to have different item labels
shown to different questionee based on some prior behaviour inside the app. 

- One of more frequent reasons for that - especially in languages with distinct
grammatical genders - is to present questionee a version of item aligned to the
gender that the questionee identifies with. 
- Reactive label updating can also be handy if the questionnaire is a part of 
experiment, and you want them to be different between varying experimental groups.

- Let's suppose, that we want to create a questionnaire, in which the questionee
is asked to describe themselves from the perspective of the third person. In the
source file for created questionnaires we will then include the 'default', 
gender-neutral noun *them*.

    ```{yaml gender_source, eval = F}
    test1:
      type: textInput
      mandatory: true
      label: What adjective would be most accurate to describe them?
      placeholder: One adjective
      width: 500px
    test2:
      type: radioButtons
      label: What is your opinion of they?
      mandatory: true
      choices:
        - Goob
        - Neutral
        - Bad
      maxItems: 1
    test3:
      type: selectizeInput
      label: What are their favourite days in the week? (max three)
      mandatory: true
      choices:
        - Monday
        - Tuesday
        - Wednesday
        - Thursday
        - Friday
        - Saturday
        - Sunday
      maxItems: 3
    ```

- We can create a select input somewhere in our shinyApps UI, that will be asking
questionee about the gender they are identifying with:

    ```{r gender_input, eval = F}
    selectizeInput(
      "gender",
      "Which gender are you identyfing as?",
      choiceNames = c("Male", "Female", 
                      "I identify as neither of above", "Prefer not to say"),
      choiceValues = c("M", "F", "O", "NI"),
      # to make no initial selection
      selected = character(0),
      multiple = T,
      options = list(maxItems = 1)
    )
    ```
    
- We need to create additional source file telling the *Quetzio* which
label should be presented for every value of the variable it should be reacting
to. Source file can be created as a R object (*data.frame* or *list*), *YAML* 
file or a *googlesheet* sheet. For clarity in this vignette YAML will be presented:

    ```{yaml gender_update_source, eval = F}
    test1:
       M: What adjective would be most accurate to describe him?
       F: What adjective would be most accurate to describe her?
    test2:
       M: What is your opinion of him?
       F: What is your opinion of her?
    test3:
       M: What are his favourite days in the week? (max three)
       F: What are her favourite days in the week? (max three)
    ```
    
>If the reactive passed as a trigger contains value not represented in the label 
update source, then the default labels will be shown.

- When everything is set, we can then create our questionnaire and its
reactivity within the server. It can be done by utilizing the function
*Quetzio_label_update()*

    ```{r gender_update_input, eval=F}
    # define the questionnaire which will have reactive labels
    questionnaire <- Quetzio_create(
      source_method = "yaml",
      source_yaml = "path/to/main/source.yaml",
      module_id = "quetzio_to_react"
    )
    
    # update_labels() method takes a reactive as a trigger, so we need to
    # pass the input value accordingly
    gender_react <- reactive(input$gender)
    
    # call the function passing your Quetzio object and reactive as a trigger
    Quetzio_label_update(
      Quetzio = questionnaire,
      trigger = gender_react, # reactive needs to be passed without parentheses!
      source_method = "yaml",
      source_yaml = "path/to/label/source.yaml"
    )
    ```
    
- You can also use answer from another questionnaire - we can utilize the 
demographic questionnaire created above. Be aware, that the answers are present
within the *Quetzio$answers()* only after the questionnaire submission!

    ```{r gender_update_quetzio, eval = F}
    gender_react <- reactive(
      demo_quetzio$answers()$gender
    )
    
    Quetzio_label_update(
      Quetzio = questionnaire,
      trigger = gender_react, # reactive need to be passed without parentheses!
      source_method = "yaml",
      source_yaml = "path/to/label/source.yaml"
    )
    ```
